Supplemental Material for ``Assessing United States county-level exposure for research on tropical cyclones and human health"

### 2019-10-13 tables/metric_definitions.tex
Work on writing

\begin{table}%[tbhp] 
\centering 
\caption{Exposure metrics considered to assess county-level exposure to 
tropical cyclones}
\begin{tabular}{p{0.9cm}p{2.5cm}p{9cm}} 
Metric & Available & Criteria for exposure \\ \midrule 
Distance & 1988--2015 & County population mean center within 100 kilometers of storm track \\ 
Rain & 1988--2011 & County cumulative rainfall of 75 millimeters or more over the period from two days before to one day after the storm's closest approach and county population mean center within 500 kilometers of the storm track \\ 
Wind & 1988--2015 & Modeled maximum sustained wind speed at the county's population mean center 15 meters per second or higher during the storm\\ 
Flood & 1996--2015 & Flood event listed in the National Oceanic and Atmospheric Administration (NOAA) Storm Events database for the county with a start date within two days of the storm's closest approach and county population mean center within 500 kilometers of the storm track \\
Tornado & 1996--2015 & Tornado event listed in the NOAA Storm Events database for the county with a start date within two days of the storm's closest approach and county population mean center within 500 kilometers of the storm track\\
\bottomrule 
\end{tabular} 
\label{tab:exposuremetrics} 
\end{table}

>>>>

\begin{table}%[tbhp] 
\centering 
\caption{Exposure metrics considered to assess county-level exposure to 
tropical cyclones}
\begin{tabular}{p{0.9cm}p{2.5cm}p{9cm}} 
Metric & Available & Criteria for exposure for binary analysis \\ \midrule 
Distance & 1988\,--\,2015 & County population mean center within 100 kilometers of storm track \\ 
Rain & 1988\,--\,2011 & County cumulative rainfall of 75 millimeters or more over the period from two days before to one day after the storm's closest approach and county population mean center within 500 kilometers of the storm track \\ 
Wind & 1988\,--\,2015 & Modeled maximum sustained wind speed at the county's population mean center 15 meters per second or higher during the storm\\ 
Flood & 1996\,--\,2015 & Flood event listed in the National Oceanic and Atmospheric Administration (NOAA) Storm Events database for the county with a start date within two days of the storm's closest approach and county population mean center within 500 kilometers of the storm track \\
Tornado & 1996\,--\,2015 & Tornado event listed in the NOAA Storm Events database for the county with a start date within two days of the storm's closest approach and county population mean center within 500 kilometers of the storm track\\
\bottomrule 
\end{tabular} 
\label{tab:exposuremetrics} 
\end{table}

### 2019-10-13 writing/darlings_intro.tex
Work on writing

>>>>

, including Sandy in 2012 (e.g., \parencite{swerdel2014}) and Katrina
in 2005 (e.g., \parencite{burton2009health}),

A recent review highlights the need to supplement these single-storm studies
with multi-year, multi-storm studies, to identify patterns that are common
across multiple storms [ref]. While multi-year studies of hurriance mortality
impacts have been conducted using disaster surveillance data, studies based on
administrative data could identify risks for non-accidental mortality and
morbidity that those studies likely undercount [ref]. Multi-storm studies with
administrative data require exposure assessment that is consistent across time
and space, allowing the administrative data to be linked to disaster exposure
[ref]. Key to expanding tropical cyclone epidemiology are therefore exposure
assessment methods that appropriately capture hazards of the storm that are
relevant to human health, methods that can be applied consistently across
multiple storms, locations, and years.

If a study misclassifies exposure to the hazard or hazards that cause the
health risk being studied, the study will generate biased estimates of tropical
cyclone risks and impacts. Further, when different studies use different
methods to assess exposure to tropical cyclones, their results are difficult to
meaningfully compare and aggregate. If different methods identify
similar sets of communities as ``exposed'',  these concerns are less serious.
However, if different methods differ substantially in which communities they
identify as ``exposed'', it makes it very important that epidemiological
studies are thoughtful in how they assess exposure.

 and
measured how well exposure classification agreed across these five metrics in
terms of classifying specific counties as exposed to a tropical cyclone.

### 2019-10-13 writing/ehp_discussion.tex
Work on writing

Epidemiological studies can help characterize which health risks are elevated
during disasters, to what degree, and to whom [Ibrahim editorial; Noji paper].
As a result, these studies help improve disaster preparedness and response
[Noji paper].  However, tropical cyclones are multi-hazard events, making it
complicated to measure exposure.  Here, we provide open-source county-level
data on multiple tropical cyclone exposure metrics and explore limitations in
that data.

@@

For the flooding events data, we found that flood event status determined based
on the NOAA Storm Events listings often agreed with measurements from \ac{USGS}
streamgages, with a flood event more likely to be listed if a storm elevated
stream flows in the county (Figure~\ref{fig:floodcomparison}).  However, there
are differences between the two flooding datasets, and these highlight both the
difficulty of measuring flood exposure at the county level and inherent
challenges in using data from a storm event database for epidemiologic exposure
assessment.

For example, there was one storm in Fulton County, GA, for which there was high
streamflow but not an associated flood event listing (Hurricane Ida, 2009).
This storm occurred in November 2009, following a month with historic rainfall
and flooding in Georgia \parencite{shepherd2011overview}.  Therefore, in this
case the flooding associated with Ida was incorporated into an ongoing flood
event listing, with a start date well before the five-day window used to
temporally match storm event listings with tropical cyclone tracks used here.

This disagreement highlights the difficulty of large-scale pairing of storm
tracks with storm event listings---without criteria for temporally matching
event dates to storm tracks, it is likely that many false positives would be
captured, for which the occurrance of a storm in the midst of an ongoing storm
event listing would be improperly attributed to the storm.  However, distance
and time restrictions, like those we used in matching NOAA Storm Event listings
with tropical storm locations and dates, do create the opportunity for
occasional false negatives, as for Hurricane Ida in Fulton County, GA, where a
storm contributes meaningfully to an ongoing event, but the event is not
captured for the storm.

@@

We found that agreement was typically low across hazard-specific tropical
exposure classifications, and agreement was also typically low between
distance-based tropical cyclone exposure assessment and each of the single
hazard-specific exposures (Figures~\ref{fig:ivanexposure}\,--\,
\ref{fig:jaccard} and S4\,--\,S5). This suggests that the use of a
distance-based metric to assess exposure to any of these hazards, or the use of
measurements from one hazard as a proxy for exposure to any of the other
hazards considered, would often be problematic, introducing exposure
misclassification.

@@

However, we did find a small set of tropical cyclones for which for which
agreement was high across single-hazard exposure assessments (e.g., Floyd
in~1999, Irene in 2011, Hannah in~2008, Bertha in~1996;
Figure~\ref{fig:jaccard}).  Hurricanes Floyd in~1999 (Figure~S4) and Irene
in~2011 both made their first \ac{US} landfall in North Carolina at minor
hurricane windspeeds (Category~2 and~1, respectively) and then skimmed the
eastern coast of the \ac{US} north through New England, bringing substantial
rainfall to much of the eastern coast from North Carolina north and causing
extensive inland flooding in North Carolina (Floyd) and New England
(Irene)~\parencite{avila2013atlantic, lawrence2000atlantic}.  Hurricanes Hannah
in~2008 and Bertha in~1996 followed the eastern coastline north of North
Carolina in a pattern similar to Floyd and Irene. For this set of storms, the
tropical cyclones' persistent proximity to water may have helped maintain wind
speeds in similar patterns to rain and distance-based exposure assessments,
resulting in more similarities across exposure assessments compared to the
other tropical cyclones we considered.

Since exposure assessments often differ across storm hazards, as well as
between each storm hazard and a distance-based proxy measurement, exposure
misclassification is a potential risk. For some studies, such exposure
misclassification might plausibly be differential (i.e., associated with the
outcome of interest or with factors associated with risk of the outcome of
interest).  For example, tropical cyclone wind exposures tend to be
concentrated in counties near the coast, while tropical cyclone wind exposures
sometimes extend well inland.  If the etiologically-relevant exposure for a
health outcome is extreme rainfall but exposure is classified based on
measurements of wind, the probability of being misclassified as unexposed would
be higher in inland counties, while the probability of being misclassified as
exposed would be higher in coastal counties. If coastal counties differ from
inland counties in either the outcome of interest or in factors associated with
risk of that outcome, exposure misclassification would be
differential~\parencite{savitz2016interpreting}.  Such differential exposure
misclassification could bias estimates of tropical cyclone effects either
towards the null (estimating a lower or null association compared to the true
association that exists) or away from the null (estimating a larger association
than actually exists)~\parencite{savitz2016interpreting, armstrong1998effect}.
[Variation across studies in how exposure is assessed?]

@@

The case study illustrates how differences in exposure assessment
across storm exposure metrics can result in differing conclusions. In this 
case, we found differences in estimates of expected
physical exposure to tropical cyclones among a population when exposure
assessment was based on different storm exposure metrics
(Figure~\ref{fig:topelecdependexposure}).

These results are informative because previous assessments of physical exposure
to tropical cyclones have often concentrated on storm winds and storm
proximity. For example, a global study of exposure and vulnerability to natural
hazards used a combination of windspeed above a certain threshold and distance
from the storm's track to assess exposure~\parencite{peduzzi2009assessing}.
While many storm impacts might be most strongly linked to wind hazards, there
is a growing recognition of the potential risks of adverse health outcomes and
property damage from rain- and flood-related tropical cyclone hazards in the
\ac{US}~\parencite{smith2009}.  Assessments based solely on wind and distance
from the storm track therefore may underemphasize potentially dangerous
exposures to certain regions of the \ac{US}, particularly inland locations.

In fact, based on our assessment of physical exposures to tropical cyclones
among electricity-dependent Medicare beneficiaries, the highest expected
physical exposure under any metric was measured for Philadelphia County, PA,
under the flood metric (Figure~\ref{fig:topelecdependexposure}).  While this
county has a similar-sized population of electricity-dependent Medicare
beneficiaries as Miami-Dade County, FL
(Figure~\ref{fig:topelecdependexposure}), the inland county of Philadelphia has
frequent storm-related flood events, which results in a very high expected
physical exposure among electricity-dependent Medicare beneficiaries in the
county. This exposure is poorly captured by most of the other exposure metrics,
under which Philadelphia County is not included in the top ten counties for
physical exposure~(Figure~\ref{fig:topelecdependexposure}).

>>>>

Epidemiological studies can help characterize which health risks are elevated
during disasters, to what degree, and to whom [Ibrahim editorial; Noji paper].
\parencite{ibrahim2005unfortunate, noji2005disasters}.  As a result, these studies help improve
disaster preparedness and response \parencite{noji2005disasters}.  However,
tropical cyclones are multi-hazard events, making it complicated to measure
exposure.  Here, we provide open-source county-level data on multiple tropical
cyclone exposure metrics and explore limitations in that data.

@@

For the flooding data, we found that flood event status determined based
on the NOAA Storm Events listings often agreed with measurements from \ac{USGS}
streamgages, with a flood event more likely to be listed if a storm elevated
streamflow across the county (Figure~\ref{fig:floodcomparison}).  However, there
are differences between the two flooding datasets, and these highlight both the
difficulty of measuring flood exposure at the county level and inherent
challenges in using data from a storm event database for epidemiologic exposure
assessment.

For example, there was one storm in Fulton County, GA, for which there was high
streamflow but not an associated flood event listing (Hurricane Ida, 2009).
This storm occurred in November 2009, following a month with historic rainfall
and flooding in Georgia \parencite{shepherd2011overview}.  Therefore, in this
case the flooding associated with Ida was incorporated into an ongoing flood
event listing, with a start date well before the five-day window we used to
temporally match storm event listings with tropical cyclone tracks.

This disagreement highlights the difficulty of large-scale pairing of storm
tracks with storm event listings---without criteria for temporally matching
event start dates to storm dates, many false positives would be
captured, for which the occurrance of a storm in the midst of an ongoing storm
event listing would be improperly attributed to the storm.  However, distance
and time restrictions, like those we used in matching NOAA Storm Event listings
with tropical storm locations and dates, do create the opportunity for
occasional false negatives, as for Hurricane Ida in Fulton County, GA, where a
storm contributes meaningfully to an ongoing event, but the event is not
captured for the storm in the exposure data.

@@

We found that tropical cyclones tended to bring different hazards to 
different counties and also that agreement was typically low between
distance-based tropical cyclone exposure assessment and each of the single
hazard-specific exposures (Figures~\ref{fig:ivanexposure}\,--\,
\ref{fig:jaccard} and S4\,--\,S5). This suggests that the use of a
distance-based metric to assess exposure to any of these hazards, or the use of
measurements from one hazard as a proxy for exposure to any of the other
hazards considered, would often be problematic, introducing exposure
misclassification.

@@

Therefore for most tropical cyclones, since exposure assessments often differ
across storm hazards, as well as between each storm hazard and a distance-based
proxy measurement, exposure misclassification is a potential risk. For some
studies, such exposure misclassification might plausibly be differential (i.e.,
associated with the outcome of interest or with factors associated with risk of
the outcome of interest).  For example, tropical cyclone wind exposures tend to
be concentrated in counties near the coast, while tropical cyclone wind
exposures sometimes extend well inland.  If the etiologically-relevant exposure
for a health outcome is extreme rainfall but exposure is classified based on
measurements of wind, the probability of being misclassified as unexposed would
be higher in inland counties, while the probability of being misclassified as
exposed would be higher in coastal counties. If coastal counties differ from
inland counties in either the outcome of interest or in factors associated with
risk of that outcome, exposure misclassification would be
differential~\parencite{savitz2016interpreting}.  Such differential exposure
misclassification could bias estimates of tropical cyclone effects either
towards the null (estimating a lower or null association compared to the true
association that exists) or away from the null (estimating a larger association
than actually exists)~\parencite{savitz2016interpreting, armstrong1998effect}.
[Variation across studies in how exposure is assessed?]

However, we did find a small set of tropical cyclones for which for which
agreement was high across several single-hazard exposure assessments (e.g.,
Floyd in~1999, Irene in 2011, Hannah in~2008, Bertha in~1996; Ernesto in~2006
Figure~\ref{fig:jaccard}).  Hurricanes Floyd in~1999 (Figure~S4) and Irene
in~2011 both made their first \ac{US} landfall in North Carolina at minor
hurricane windspeeds (Category~2 and~1, respectively) and then skimmed the
eastern coast of the \ac{US} north through New England, bringing substantial
rainfall to much of the eastern coast from North Carolina north and causing
extensive inland flooding in North Carolina (Floyd) and New England
(Irene)~\parencite{avila2013atlantic, lawrence2000atlantic}.  Hurricanes Hannah
in~2008, Bertha in~1996, and Ernesto in~2006 also followed the eastern
coastline. For this set of storms, the tropical cyclones' persistent proximity
to water may have helped maintain wind speeds in similar patterns to rain and
distance-based exposure assessments, resulting in more similarities across
exposure assessments compared to the other tropical cyclones we considered.
For these storms, it may be possible to assess exposure to multiple hazards of
the storm using a single metric, in some cases even a proxy like the distance
between a county and the storm's track.  However, for these storms it may be
difficult to try to untangle the contribution of each hazard to the overall
effect of the storm, given that several hazards have similar geographical
patterns.

@@

The case study illustrates how differences in exposure assessment across storm
exposure metrics can result in differing conclusions. In this case, we found
differences in estimates of expected rates of physical exposure to tropical
cyclones among a population when exposure assessment was based on different
storm exposure metrics (Figure~\ref{fig:topelecdependexposure}).  These results
are informative because previous assessments of physical exposure to tropical
cyclones have often concentrated on storm winds and storm proximity. For
example, a global study of exposure and vulnerability to natural hazards used a
combination of windspeed above a certain threshold and distance from the
storm's track to assess exposure~\parencite{peduzzi2009assessing}.  While many
storm impacts might be most strongly linked to wind hazards, there is a growing
recognition of the potential risks of adverse health outcomes and property
damage from rain- and flood-related tropical cyclone hazards in the
\ac{US}~\parencite{smith2009}.  Assessments based solely on wind and distance
from the storm track therefore may underemphasize potentially dangerous
exposures to certain regions of the \ac{US}, particularly inland locations.  In
fact, based on our assessment of physical exposures to tropical cyclones among
electricity-dependent Medicare beneficiaries, the highest expected physical
exposure under any metric was measured for Philadelphia County, PA, under the
flood metric (Figure~\ref{fig:topelecdependexposure}).  While this county has a
similar-sized population of electricity-dependent Medicare beneficiaries as
Miami-Dade County, FL (Figure~\ref{fig:topelecdependexposure}), the inland
county of Philadelphia has frequent storm-related flood events, which results
in a very high expected physical exposure among electricity-dependent Medicare
beneficiaries in the county. This exposure is poorly captured by most of the
other exposure metrics, under which Philadelphia County is not included in the
top ten counties for expected rates of physical
exposure~(Figure~\ref{fig:topelecdependexposure}).

### 2019-10-13 writing/ehp_figures.tex
Work on writing

\begin{figure}%[tbhp] 
\centering 
\includegraphics[width = 0.6\linewidth]{jaccard_heatmap.pdf} 
\caption{Agreement between exposure classifications based on different
         exposure metrics for all storms between~1996 and~2011 for which 
	 at least~250 counties were exposed based on at least one metric.
	 Each row shows one storm, and the color of each cell shows the 
	 measured Jaccard index for each pair of exposure metrics 
	 (proportion of counties classified as exposed by both metrics out 
	 of storms classified as exposed by either metric). The colors to the 
	 right of the main heatmap for each storm indicate the total number of 
	 counties classified as exposed to the storm by any of the five metrics, 
	 providing an indication of each storm's extent. Storms are displayed 
	 within clusters that have similar patterns in county-level exposure 
	 agreement for metric pairs, based on hierarchical clustering using the 
	 complete link method~\parencite{murtagh2012algorithms}; columns are also 
	 ordered based on hierarchical clustering. Maps are available showing the 
	 counties identified as exposed under each of five metrics for the widest-extent 
	 storm in each cluster: Hurricane Ivan in~2004 (Figure~\ref{fig:ivanexposure}) 
	 and Hurricanes Floyd in~1999, Lee in~2011, Cindy in~2005, and Katrina 
	 in~2005 (Figure~S4).
} 
\label{fig:jaccard}
\end{figure}

@@

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=15.5cm]{topelecdependexposure}
\caption{Study counties with the highest expected physical exposure per year among
	 electricity-dependent Medicare beneficiaries for each exposure metric. 
	 The color of each bar indicates the number of Medicare beneficiaries in the 
	 county reliant on electricity-dependent medical and assistive equipment as 
	 of July~2017. The length of each bar shows the average expected physical exposure
	 to tropical cyclones among this population based on a given exposure metric, i.e., 
	 the expected number of these electricity-dependent Medicare beneficiaries exposed 
	 to tropical storms per year based on that metric.}
\label{fig:topelecdependexposure}
\end{figure*}

>>>>

\begin{figure}%[tbhp] 
\centering 
\includegraphics[width = 0.6\linewidth]{jaccard_heatmap.pdf} 
\caption{Agreement between exposure classifications based on different
         exposure metrics for all storms between~1996 and~2011 for which 
	 at least~100 counties were exposed based on at least one metric.
	 Each row shows one storm, and the color of each cell shows the 
	 measured Jaccard index for each pair of exposure metrics 
	 (proportion of counties classified as exposed by both metrics out 
	 of storms classified as exposed by either metric). The colors to the 
	 right of the main heatmap for each storm indicate the total number of 
	 counties classified as exposed to the storm by any of the five metrics, 
	 providing an indication of each storm's extent. Storms are displayed 
	 within clusters that have similar patterns in county-level exposure 
	 agreement for metric pairs, based on hierarchical clustering using the 
	 complete link method~\parencite{murtagh2012algorithms}; columns are also 
	 ordered based on hierarchical clustering. Maps are available showing the 
	 counties identified as exposed under each of five metrics for the widest-extent 
	 storm in each cluster: Hurricane Ivan in~2004 (Figure~\ref{fig:ivanexposure}) 
	 and Hurricanes Floyd in~1999, Lee in~2011, Cindy in~2005, and Katrina 
	 in~2005 (Figure~S4).
} 
\label{fig:jaccard}
\end{figure}

@@

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=15.5cm]{topelecdependexposure}
\caption{Study counties with the highest expected rate of physical exposure per year among
	 electricity-dependent Medicare beneficiaries based on each exposure metric. 
	 The color of each bar indicates the number of Medicare beneficiaries in the 
	 county reliant on electricity-dependent medical and assistive equipment as 
	 of July~2017. The length of each bar shows the average expected rate of physical exposure
	 to tropical cyclones among this population based on a given exposure metric, i.e., 
	 the expected number of these electricity-dependent Medicare beneficiaries exposed 
	 to tropical storms per year based on that metric (Table 1).}
\label{fig:topelecdependexposure}
\end{figure*}

### 2019-10-13 writing/ehp_introduction.tex
Work on writing

Recently, several major tropical cyclones have hit \ac{US} cities, including
Hurricanes Harvey, Irma, and Maria in 2017 \parencite{blake20182017} and
Hurricanes Florence and Michael in 2018 \parencite{avila20192018}. Researchers
are exploring how these storms impacted human health (e.g.,
\parencite{santos2018use, rivera2018estimating, santos2018differential,
grineski2019impact, issa2018deaths, tanz2019notes, paul2019brief}), including
through projects funded through \ac{NIH} Rapid Response grants
\parencite{nihreporter}. These projects will add to evidence from previous
hurricanes, including Sandy in 2012 (e.g., \parencite{swerdel2014}) and Katrina
in 2005 (e.g., \parencite{burton2009health}), characterizing the health impacts
of hurricanes.

A recent review highlights the need to supplement these single-storm studies
with multi-year, multi-storm studies, to identify patterns that are common
across multiple storms [ref]. While multi-year studies of hurriance mortality
impacts have been conducted using disaster surveillance data, studies based on
administrative data could identify risks for non-accidental mortality and
morbidity that those studies likely undercount [ref]. Multi-storm studies with
administrative data require exposure assessment that is consistent across time
and space, allowing the administrative data to be linked to disaster exposure
[ref]. Key to expanding tropical cyclone epidemiology are therefore exposure
assessment methods that appropriately capture hazards of the storm that are
relevant to human health, methods that can be applied consistently across
multiple storms, locations, and years.

The \ac{NHC} publishes a ``Best Tracks'' dataset that is considered the gold
standard for Atlantic-basin tropical cyclone tracks.  It records the central
position of a tropical cyclone every six hours, as well as the storm's
\underline{minimum pressure} and \underline{central maximum sustained winds}. This data is openly
available through the \ac{HURDAT2}, a post-storm assessment conducted
by the \ac{US} \ac{NHC} that incorporates data from a variety of sources,
including satellite data and, when available, aircraft reconnaissance
data~\parencite{landsea2013, jarvinen1988}. With this data, it is
straightforward to measure whether a community was in the direct path, or
within a certain distance of the path, of a storm. Some studies have indeed
used this data to assess tropical cyclone exposure based on how near the
storm's central track came to the county, either to assess average exposure
patterns to tropical storms [refs] or to characterize exposure for health
studies [refs].

@@

Further, when studies use distance from the storm's track to assess exposure,
they often use an equal buffer distance on each side of the tropical cyclone
track (e.g.,~\cite{czajkowski2011, grabich2015, grabich2016, zandbergen2009,
tansel2010}). However, the forces of a tropical cyclone tend to be distributed
around the center in a non-symmetrical way. Extreme winds are more common to
the right of the track, where counter-clockwise cyclonic winds move in concert
with the tropical cyclone's forward motion~\parencite{halverson2015}, and the
fatal tornadoes associated with \ac{US} tropical cyclones between~1995 and~2009
occurred almost exclusively to the right of the tropical cyclone's track,
mostly in the right front quadrant of the tropical
cyclone~\parencite{moore2012}. Rain, conversely, is often heaviest to the left
of the tropical cyclone's track, especially when the tropical cyclone interacts
with other weather systems~\parencite{atallah2003, atallah2007,
zhu2013variations} or undergoes an extratropical
transition~\parencite{elsberry2002}.

If a study misclassifies exposure to the hazard or hazards that cause the
health risk being studied, the study will generate biased estimates of tropical
cyclone risks and impacts. Further, when different studies use different
methods to assess exposure to tropical cyclones, their results are difficult to
meaningfully compare and aggregate. If different methods identify
similar sets of communities as ``exposed'',  these concerns are less serious.
However, if different methods differ substantially in which communities they
identify as ``exposed'', it makes it very important that epidemiological
studies are thoughtful in how they assess exposure.

To provide open-source data on tropical cyclone exposures to other researchers,
we developed a dataset of county-level exposure to tropical cyclones in all
eastern \ac{US} counties for five different metrics
(Table~\ref{tab:exposuremetrics}): (1)~distance to tropical cyclone track;
(2)~maximum sustained wind speed; (3)~cumulative rainfall; (4)~flood events;
and (5)~tornado events~\parencite{hurricaneexposure}. This data is provided at
the county level since data on many potential impacts are available at
county-level aggregations (e.g., direct hurricane-related
deaths~\parencite{czajkowski2011}; birth outcomes~\parencite{grabich2015,
grabich2016}; autism prevalence~\parencite{kinney2008}) and since decisions and
policies to prepare for, and respond to, tropical cyclones are often undertaken
at the county level~\parencite{zandbergen2009, rappaport2000}. Further, we
explored patterns in these exposure assessments across storm hazards and
measured how well exposure classification agreed across these five metrics in
terms of classifying specific counties as exposed to a tropical cyclone.

>>>>

Recently, several major tropical cyclones have hit \ac{US} cities, including
Hurricanes Harvey, Irma, and Maria in 2017 \parencite{blake20182017} and
Hurricanes Florence and Michael in 2018 \parencite{avila20192018}. Researchers
are exploring how these storms impacted human health (e.g.,
\parencite{santos2018use, rivera2018estimating, santos2018differential,
grineski2019impact, issa2018deaths, tanz2019notes, paul2019brief}), including
through projects funded by \ac{NIH} Rapid Response grants
\parencite{nihreporter}. These projects will add to evidence characterizing how
hurricanes impact human health, including evidence from multi-year studies
based on fatality data from post-disaster surveillance
\parencite{rappaport2000, rappaport2014fatalities, rappaport2016fatalities,
czajkowski2010fatal, czajkowski2011, moore2012}.

For several types of climate-related disasters---including heat waves, floods,
and wildfires---research based on surveillance data has been richly
supplemented by studies analyzing trends in community-wide administrative or
vital data, including time series or case-crossover studies (e.g.,
\cite{anderson2010heat, son2012impact, haikerwal2015impact, liu2017wildfire,
milojevic2017mental}).  These studies typically compare the daily rate of a
health outcome in a community during disasters to rates during comparable
non-disaster periods.  While these studies cannot attribute specific cases
(e.g., a specific person's death) to a disaster, they can help characterize the
community-wide change in health risk during disasters, and can help capture
impacts that might be missed or underestimated in post-disaster surveillance.
In many cases, these studies analyze multi-year, multi-community data, allowing
them to estimate average associations over many disasters and to explore how a
disaster's characteristics, or the characteristics of the community it hits,
modify associated health risk (e.g., \cite{anderson2010heat, son2012impact,
liu2017wildfire}).  Some studies have begun to use this approach to study the
health impacts of tropical cyclones, including several studies of Hurricane
Maria (e.g., \cite{santos2018use, santos2018differential}) and a study of the
2004 hurricane season in Florida \parencite{mckinney2011}.  However, to expand
this approach to study longer time periods or a larger set of communities, it
is critical that researchers be able to assess exposure to tropical cyclones in
a way that is consistent and comparable across storms, years, and communities.

The \ac{NHC} publishes a ``Best Tracks'' dataset that is considered the gold
standard for Atlantic-basin tropical cyclone tracks.  It records the central
position of a tropical cyclone every six hours, as well as the storm's minimum
central pressure and maximum wind speed.  This data is openly available through
the \ac{HURDAT2}, a post-storm assessment conducted by the \ac{US} \ac{NHC}
that incorporates data from a variety of sources, including satellite data and,
when available, aircraft reconnaissance data~\parencite{landsea2013,
jarvinen1988}. With this data, it is straightforward to measure whether a
community was in the direct path, or within a certain distance of the path, of
a storm. Some studies have indeed used this data to assess tropical cyclone
exposure based on how near the storm's central track came to the county, either
to assess average exposure patterns for tropical cyclones [refs] or to
characterize exposure for health studies (e.g., \cite{currie2013}).

@@

Further, when studies use distance from the storm's track to assess exposure,
they often use the same buffer constraints on each side of the tropical cyclone
track (e.g.,~\cite{czajkowski2011, zandbergen2009, grabich2015measuring,
tansel2010, currie2013}). However, the forces of a tropical cyclone tend to be
distributed around its center non-symmetrically. Extreme winds are more common
to the track's right, where counter-clockwise cyclonic winds move in concert
with the tropical cyclone's forward motion~\parencite{halverson2015}, and the
fatal tornadoes associated with \ac{US} tropical cyclones between~1995 and~2009
occurred almost exclusively to the right of the tropical cyclone's track,
mostly in the storm's right front quadrant~\parencite{moore2012}. Rain,
conversely, is often heaviest to the left of the track, especially when the
tropical cyclone interacts with other weather systems~\parencite{atallah2003,
atallah2007, zhu2013variations} or undergoes an extratropical
transition~\parencite{elsberry2002}.

The multi-hazard nature of tropical cyclones therefore makes it hard to assess
exposure based only on a proxy measurement, like how close the storm's central
track came to the community. While other approaches have been developed to
incorporate wind hazards into exposure assessment (e.g.,
\cite{grabich2015measuring, zandbergen2009}), but these do not incorporate other
storm hazards. To help epidemiological researchers with exposure assessment for
tropical cyclones, we here develop a dataset of county-level exposure to
tropical cyclones in all eastern \ac{US} counties, which we have packaged as an
open-source dataset~\parencite{hurricaneexposure}, as well as an associated
package of open-source functions that can be used to explore and map this data
and to link it with county-level health data~\parencite{hurricaneexposuredata}.
These data cover five metrics characterizing exposure to tropical cyclone
hazards (Table~\ref{tab:exposuremetrics}): (1)~closest distance the storm's
central track came to the county's center (a proxy measurement of storm
exposure used in some previous studies); (2)~maximum sustained wind speed at
the county's center over the course of the storm; (3)~cumulative rainfall in
the county over the course of the storm; (4)~flood events in the county
associated with the storm; and (5)~tornado events in the county associated with
the storm.  We aggregated these data at the county level since data on many
potential impacts are available at county-level aggregations (e.g., direct
hurricane-related deaths~\parencite{czajkowski2011}; birth
outcomes~\parencite{grabich2015, grabich2016}; autism
prevalence~\parencite{kinney2008}) and since decisions and policies to prepare
for, and respond to, tropical cyclones are often undertaken at the county
level~\parencite{zandbergen2009, rappaport2000}.

In this paper, we describe how we developed this dataset and explore how the
measurements in it compare to other data that could be used to characterize
tropical cyclone hazards in the context of epidemiological studies.  Further,
we explore and present patterns in binary exposure assessments based on these
measurements, both for each individual metric and in terms of agreement between
metrics. These analyses can help epidemiologists as they develop study designs
and plan statistical analysis for multi-year, multi-community studies that
investigate how community-wide rates of health outcomes change during exposure
to the hazards brought by tropical cyclones. These analyses can also help
researchers compare and interpret results from previous epidemiological studies
that have assessed tropical cyclone exposure in different ways, helping to
[synthesize] previous epidemiologic results to form a better picture of how
these storms can affect human health.
